### 2012-11-14 ASA2013/asa2013.tex
la2pdf commit - 2012:11:14	20:38:41	(Wed14.Nov)

\begin{abstract}
The use of adaptive beamformers in active sonar use of a Minimum Variance (MV) beamforming have demostrated

The quality of active sonar images can be improved by the use of a Minimum Variance (MV) beamformer.

Several studies have shown that using a Minimum Variance (MV) beamformer when forming active sonar images

The Minimum Variance Distortionless Reponse (MVDR) beamformer has lately been applied to active sonar imaging. It displays a potential for improving the image quality beyond the limits of conventional methods, but rely on the estimation and inversion of a spatial covariance matrix. This translates to a complexity that is cubic with the number of elements $M$, O($M^3$), major complexity involved,  its use is discouraged due to its major computational complexity and need for robustification. This is because it involves the estimation and inversion of a spatial covariance matrix,

@@

\section{Introduction}

>>>>

\begin{abstract}
The Minimum Variance Distortionless Reponse (MVDR) beamformer has lately been applied to active sonar imaging. While displaying an ability to improve the image quality beyond the limits of conventional beamformers, it relies on the estimation and inversion of a spatial covariance matrix for each the image pixels. This may discourage its use, since robustification methods must be introduced to ensure numerical and statistical validity, and the computational complexity is cubic with the number of elements, O($M^3$).

We will show that for systems with less than $M$=32 channels, the estimation process is the main bottleneck. In this case, we suggest arithmetic optimizations for the estimation step, and explain how the the MVDR can be mapped to a high-end GPU to yield processing rates of more than 1\,Mpx/s. When $M$ exceeds 32, the inversion step dominates, and

This represents a speedup of 2-3 orders of magnitude over a moderately optimized C and Matlab reference implementation. For higher channel systems, we employ MVDR beamspace processing on the GPU

 With a channel count that exceeds 32, we show that we switch to using frequency based methods we run on a some algorithmic optimizations and porting of the  to a GPU

Depending on the number of channels in the system, we target these issues in 3 different ways.

  The computational complexity involved, as well as the need to introduce robustification techniques to make  This may discurage its use, since the estimation process requires  process The computational complexity involved, and the means required to make the well suited,

Obtaining a robust estimate This translates to a complexity that is cubic with the number of elements $M$, O($M^3$), major complexity involved,  its use is discouraged due to its major computational complexity and need for robustification. This is because it involves the estimation and inversion of a spatial covariance matrix,

@@

% \section{Introduction}
